### 2019-04-15 manuscript.tex
Update manuscript.tex

Social norm is a fundamental approach in comprehending and intervening FGC practice \cite{DuncWand11, EffeVogt15, Hayf05, Mack96, Mack00, Youn02} while other perspectives (e.g., human rights and feminist theory \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} entails reasons of negotiating and abolishing the practices.  Convention theory posits FGC an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe09}.  FGC was also viewed as a social capital for inclusion and exclusion within women’s social groups \cite{Shel-Wand11}.  When the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09, ThomMadd92} and the bond within women's social networks could be intergenerational, interdependent and interconnected across generations and genders was proposed intervention of FGC  \cite{Mack00, DuncWand11, ShelWand11}. \cfonly{add \cite{Bicc15}}

@@

@@

Identifying benefits of FGC practice is crucial to promote sustainable change \cite{EffeVogt15}.  This study takes both the dynamics of beliefs of FGC benefits and of FGC practices into account at both a population and a community level to understand associations of FGC values and intention of carrying out the practices l \cite{BoylCorl010, Drol11,Hayf05, Grue05, Hodg11,KandNwak09, OdukAfol17} (to confirm).  We developed three models in this study.  The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and intention to cut daughters in the hope that if patterns of social norms (i.e., aggregation of values of FGC benefits) associating behavioral intention can be detected.  Additionally, we also decompose the model into two “structural” models:  “persistence” model to study women’s beliefs of FGC benefits and FGC continuance; and “future” model to examine the association of beliefs of FGC benefits, FGC persistence and intention of cutting daughters to understand how such positions change the main model.

@@

The main response variables were woman's intention to cut their daughters in the daughter model and the daughter-future model, and woman's attitude on whether FGC should be continued in the FGC future model.  The predictors were selected based on literature and three main theories which have developed to account for the practice of FGC (i.e., convention theory, feminist theory and modernization theory) \cite{Fay05, BellNova15}.  The main predictors were woman's FGC status, beliefs of FGC benefits and attitudes of gender equality.  Other socio demographic variables were also included:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, media and residence (urban vs. rural) in addition to country.  The followings were treated as random variables:  cluster ID (villages) and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it).

In order to address the significance of community impact on the practice of FGC, education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence were also tested at the community level \cfcmt{on a cluster level, not national, right?} in response to the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, Moor13, OdukAfol17, Youn02}).}).  Cluster  was used to represent a community level of impact \cite{AligRen06, Hayf05}

@@

We used cumulative link mixed models (CLMMs) in the statistics package R \cite{Rstats,Rpackage_ordinal} to analyze the models.  The CLMM framework allows us to model a binary or ordinal response variable (i.e., intention of cutting daughters and whether to continue FGC practice), while treating clusters and ethnicity as random effects.

@@

Our findings showed that women’s decision on cutting their daughters was clearly related to their own FGC status, personal beliefs of FGC benefits and theFGC prevalent in their community \cf{link}; yet group beliefs of FGC benefits in their community did not play a clear role in determining whether a daughter would be cut.  The similar results also applied to women’s view of whether FGC should be continued \cf{link}.  \cfjd{How to use the future-mother producing daughter model?}.  Our findings suggest that FGC practice is a social norm in respect of how an individual behavioral intention on FGC is in line with how their community implement this ritual; the social norm is based on what an agent perceives what their community members think and that perception can be based on the members’ behavioural outcome (i.e., whether others had FGC) or communication about the ritual practice \cite{} .

@@

- community level of effects -
\cite{ChegAske04}(community -based approach), \cite{BrowBeec13, Hayf05, KandShel19, PatrSing15, ShelWand11}
\cite{BellNova15}: "We find that much of the variation in a woman's support for FGC can be attributed to individual- and household-level factors rather than to village-level factors or to factors beyond the village level."
- tipping point/threshold -
\cfcmt{empirical norm:  enough others follow the norm-  community level of FGC \cite{Bicc10} normative norm:  enough others think we need to follow the norm -  FGC beliefs, decision on daughter's FGC status (already and future), \cite{Bicc10}}
— secondary analysis/socio demograhpic —

@@

\cite{MashMatt09} (In Ethiopia):  Women who believed that FGM should continue were more likely to be aged 15-24years; rural residents; Muslim; married ; uneducated ; circumcised ; and to have had no exposure to mass media
\cite{DalaKalm18}(in 7 African countries): increasing media coverage and education, and reducing poverty are of importance for shifting adolescent girls' attitudes in favor of discontinuation of FGM.
\cite{Hayf05, PashPonn16} (more)
% education:  \cite{IliyAbub12, KarmKand11}
% religion:  \cite{KarmKand11}

@@

% little support for seeing FGC a prerequisite for marriage or related to marrying well, but peer pressure was an important factor on FGC decision (i.e., peer convention instead of marriage convention.) \cite{DuncWand11}
% when influences from within the communities are strong, individuals tend to self-enforce norms of what the community expect from their behaviours \cite{Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09}. (from the introduction.  try to compare our result with theirs).
% mother-daughter: \cite{PashPonn16}

>>>>

Social norm is a fundamental approach in comprehending and intervening FGC practice \cite{DuncWand11, EffeVogt15, Hayf05, Mack96, Mack00, Youn02} while other perspectives (e.g., human rights and feminist theory \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} entails reasons of negotiating and abolishing the practices.  Convention theory posits FGC an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe08}.  FGC was also viewed as a social capital for inclusion and exclusion within women’s social groups \cite{Shel-Wand11}.  When the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe08, ThomMadd92} and the bond within women's social networks could be intergenerational, interdependent and interconnected across generations and genders was proposed intervention of FGC  \cite{Mack00, DuncWand11, ShelWand11}. \cfonly{add \cite{Bicc15}}

@@

% prevalence of FGC in those 4 nations.

@@

Identifying benefits of FGC practice is crucial to promote sustainable change \cite{EffeVogt15}.  This study takes both the dynamics of beliefs of FGC benefits and of FGC practices into account at both a population and a community level to understand associations of FGC values and intention of carrying out the practices l \cite{BoylCorl010, Drol11,Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, OdukAfol17} (to confirm).  We developed three models in this study.  The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and intention to cut daughters in the hope that if patterns of social norms (i.e., aggregation of values of FGC benefits) associating behavioral intention can be detected.  Additionally, we also decompose the model into two “structural” models:  “persistence” model to study women’s beliefs of FGC benefits and FGC continuance; and “future” model to examine the association of beliefs of FGC benefits, FGC persistence and intention of cutting daughters to understand how such positions change the main model.

@@

Our main interest in this project is to study how norms associate with behavioural intention.  We focus on how women will likely cut their daughters or not based on their current intention and that provide a more convincing result on how FGC norms affect FGC practice than using than what had already happened (e.g. women’s own FGC status).  Therefore, our main response variables were woman's behavioural intention to cut their daughters in the daughter model and the mixed (daughter-future) model, and woman's attitude on whether FGC should be continued in the FGC persistence model.  The predictors were selected based on literature and three main theories which have developed to account for the practice of FGC (i.e., convention theory, feminist theory and modernization theory) \cite{Fay05, BellNova15}.  The main predictors were woman's FGC status, beliefs of FGC benefits and attitudes of gender equality.  Beliefs of FGC benefits was estimated based on a list of questionnaires (see supp) and quantified using PCA in order to identify which benefit was mostly recognized in connection norm.  Other socio demographic variables were also included:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, media and residence (urban vs. rural) in addition to country.  The followings were treated as random variables:  cluster ID (villages) and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it).

In order to address the significance of community impact on the practice of FGC, education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence were also tested at the community level \cfcmt{on a cluster level, not national, right?} in response to the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, Moor13, OdukAfol17, Youn02}).}).  Cluster  was used as a proxy to represent a community level of impact \cite{AligRen06, Hayf05, Krav02}

@@

We used cumulative link mixed models (CLMMs) in the statistics package R \cite{Rstats,Rpackage_ordinal} to analyze the models.  The CLMM framework allows us to model a binary or ordinal response variable (i.e., intention of cutting daughters and whether to continue FGC practice), while treating clusters and ethnicity as random effects.  
We subtracted respondent (-1) from the cluster when testing the community effect \cfjd{Please rewrite this. Also, do we need to mention how we treat cluster with only one sample (if that happens).}

@@

Our findings suggest that a daughter’s likely future of being cut or not is overdetermined by her community’s overall likelihood of mothers’ intention of cutting their daughters, fgc prevalence, among others.  Our findings show that omen’s decision on cutting their daughters was clearly related to their own FGC status, personal beliefs of FGC benefits and theFGC prevalent in their community \cf{link}; yet group beliefs of FGC benefits in their community did not play a clear role in determining whether a daughter would be cut.  The similar results also applied to women’s view of whether FGC should be continued \cf{link}.  \cfjd{How to use the future-mother producing daughter model?}.  Our findings suggest that FGC practice is a social norm in respect of how an individual behavioral intention on FGC is in line with how their community implement this ritual; the social norm is based on what an agent perceives what their community members think and that perception can be based on the members’ behavioural outcome (i.e., whether others had FGC) or communication about the ritual practice \cite{} .

@@

- community level of effects -
\cite{ChegAske04}(community -based approach), \cite{BrowBeec13, Hayf05, KandShel19, PatrSing15, ShelWand11}
\cite{BellNova15}: "We find that much of the variation in a woman's support for FGC can be attributed to individual- and household-level factors rather than to village-level factors or to factors beyond the village level."
- tipping point/threshold -
\cfcmt{empirical norm:  enough others follow the norm-  community level of FGC \cite{Bicc10} normative norm:  enough others think we need to follow the norm -  FGC beliefs, decision on daughter's FGC status (already and future), \cite{Bicc10}}

- Beliefs of FGC benefits -
Our PCA results show that women’s beliefs of what benefits FGC brings is not clearly identified (see figure pca) and marriageability was not a clear one (to compare with \cite{Mack?,}.  On interpretation is that marriageability is no longer a strong belief in community where FGC is still common and new norms are insinuated around \cite{EffeVogt15, MackLeJe08, ShelWand11, networking, part of social groups Duncan-Shell?}

— secondary analysis/socio demograhpic —

@@

\cite{MashMatt09} (In Ethiopia):  Women who believed that FGM should continue were more likely to be aged 15-24years; rural residents; Muslim; married ; uneducated ; circumcised ; and to have had no exposure to mass media
\cite{DalaKalm18}(in 7 African countries): increasing media coverage and education, and reducing poverty are of importance for shifting adolescent girls' attitudes in favor of discontinuation of FGM.
\cite{Hayf05, PashPonn16} (more)
% education:  \cite{IliyAbub12, KarmKand11}
% religion:  \cite{HayfTrin11, KarmKand11}

@@

% little support for seeing FGC a prerequisite for marriage or related to marrying well, but peer pressure was an important factor on FGC decision (i.e., peer convention instead of marriage convention.) \cite{DuncWand11}
% when influences from within the communities are strong, individuals tend to self-enforce norms of what the community expect from their behaviours \cite{Hayf05, KandNwak09, Mack96, Mack06, MackLeJe08}. (from the introduction.  try to compare our result with theirs).
% mother-daughter: \cite{PashPonn16}
